\LARGE \bf Towards a Data-driven Approach to Motion Planning

### 2014-09-30 paper2015asml.tex
more fixes

The planning algorithms that were used were RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: \sc{PathLength} and \sc{MaxMinClearance}.The objective for \sc{PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for \sc{MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\ref{OMPL:2012}.

>>>>

The planning algorithms that we used are RRT-Connect~\cite{kuffner2000rrt} and RRT*.  RRT*~\cite{frazzoli-RRTstar} was used with two different cost functions: {\sc PathLength} and {\sc MaxMinClearance}.The objective for {\sc PathLength} minimizes the length of the trajectory (as the sum of the euclidean distances between ends of trajectory segments). The objective for {\sc MaxMinClearance} computes uses the minimum clearance of a configuration belonging to a trajectory as the value it is trying to maximize. Both planners are implemented in the OMPL library~\ref{OMPL:2012}.
